~\Large Increased sexual dimorphism evolves in a fossil stickleback following ecological release from fish piscivores

### 2024-10-21 manuscript/paper.tex
YS. editing, revising, and adding to the manuscript.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{setspace} \setstretch{1.15} \usepackage{float} \floatplacement{figure}{t}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={cyan},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={cyan},
  pdfcreator={LaTeX via pandoc}}

@@

THIS FIGURE DOESN'T SHOW MUCH. LET'S CUT FOR SPACE.

{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-2-1}

\caption{Fossil sample size for each time period}\label{fig:unnamed-chunk-2}
\end{figure}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3492}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1905}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4603}}@{}}
\caption{Traits and trait descriptions. `sc' denotes size correction of
trait against standard length. Names of bones follow Bowne
(\protect\hyperlink{ref-Bowne1994}{1994}) unless otherwise
noted.}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Trait Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Code
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Description
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Trait Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Code
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Description
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Standard Length & \texttt{stl} & Distance from anterior tip of
premaxilla to posterior end of last vertebra (hypural plate) \\
Dorsal Spine & \texttt{mds} & Number of dorsal spines from 0 to 3 \\
Dorsal Fin Ray & \texttt{mdf} & Number of bones in the dorsal fin
posterior to the third dorsal spine (i.e., soft dorsal fin rays) \\
Anal Fin Ray & \texttt{maf} & Number of bones in the anal fin posterior
to the anal spine (i.e., soft dorsal fin rays) \\
Abdominal Vertebra & mav & Number of vertebrae anterior to the first
vertebra contacting an anal fin pterygiophore (Aguirre et al.~2014) \\
Caudal Vertebra & \texttt{mcv} & Number of vertebrae posterior to and
including the first vertebra contacting an anal fin pterygiophore
(Aguirre et al.~2014) \\
Pterygiophore number & \texttt{mpt} & Number of pterygiophores anterior
to but excluding the pterygiophore under the third dorsal spine, which
is immediately anterior to and contiguous with the dorsal fin \\
Pelvic Spine length & \texttt{lps.sc} & Length from the base of one
pelvic spine above its articulation with the pelvic girdle to its distal
tip \\
Ectocoracoid & \texttt{ect.sc} & Length between the anterior and
posterior tips of the shoulder girdle base (i.e., ectocoracoid) \\
Pelvic Girdle & \texttt{tpg.sc} & Length between the anterior to
posterior tips along midline. If vestigial, the sum of longest
anterior-posterior axis for the vestiges \\
Cleithrum length & \texttt{cle.sc} & Length from free dorsal tip to
ventral tip of the cleithrum on the anterior margin of the shoulder
girdle (i.e., cleithrum) \\
Premaxilla & \texttt{pmx.sc} & Length from the anterior tip of the
premaxilla to the distal tip of the ascending process of the
premaxilla \\
Dorsal Spine & \texttt{Ds\#.sc\#\ =\ 1,2,or\ 3} & Length from the base
of a dorsal spine above the pterygiophore to its distal tip along the
anterior edge \\
Pterygiophore & \texttt{lpt.sc} & Distance between the anterior to
posterior tips of the pterygiophore immediately preceding the 3rd dorsal
spine (when present) \\
\end{longtable}

@@

All models were built using Team
(\protect\hyperlink{ref-R2022language}{2022}) and (\textbf STAN)

@@

\toprule\noalign{}

@@

\midrule\noalign{}

@@

\bottomrule\noalign{}
\endlastfoot

@@

@@

\caption{cle}\label{fig:unnamed-chunk-7}
\end{figure}
\begin{figure}

@@

\caption{ds1}\label{fig:unnamed-chunk-8}
\end{figure}
\begin{figure}

@@

\caption{ds2}\label{fig:unnamed-chunk-9}
\end{figure}
\begin{figure}

@@

\caption{ds3}\label{fig:unnamed-chunk-10}
\end{figure}
\begin{figure}

@@

\caption{ect}\label{fig:unnamed-chunk-11}
\end{figure}
\begin{figure}

@@

\caption{lps}\label{fig:unnamed-chunk-12}
\end{figure}
\begin{figure}

@@

\caption{lpt}\label{fig:unnamed-chunk-13}
\end{figure}
\begin{figure}

@@

\caption{maf}\label{fig:unnamed-chunk-14}
\end{figure}
\begin{figure}

@@

\caption{mav}\label{fig:unnamed-chunk-15}
\end{figure}
\begin{figure}

@@

\caption{mcv}\label{fig:unnamed-chunk-16}
\end{figure}
\begin{figure}

@@

\caption{mdf}\label{fig:unnamed-chunk-17}
\end{figure}
\begin{figure}

@@

\caption{mds}\label{fig:unnamed-chunk-18}
\end{figure}
\begin{figure}

@@

\caption{mpt}\label{fig:unnamed-chunk-19}
\end{figure}
\begin{figure}

@@

\caption{pmx}\label{fig:unnamed-chunk-20}
\end{figure}

@@

\caption{stl}\label{fig:unnamed-chunk-21}
\end{figure}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R2022language}{}}%
Team, R Core. 2022. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{setspace} \setstretch{1.15} \usepackage{float} \floatplacement{figure}{t}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={cyan},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={cyan},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1607}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0893}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.7500}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Trait Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Code
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Description
\end{minipage} \\
\midrule()
\endhead
Standard Length & \texttt{stl} & Distance from anterior tip of
premaxilla to posterior end of last vertebra (hypural plate) \\
Dorsal Spine & \texttt{mds} & Number of dorsal spines from 0 to 3 \\
Dorsal Fin Ray & \texttt{mdf} & Number of bones in the dorsal fin
posterior to the third dorsal spine (i.e., soft dorsal fin rays) \\
Anal Fin Ray & \texttt{maf} & Number of bones in the anal fin posterior
to the anal spine (i.e., soft dorsal fin rays) \\
Abdominal Vertebra & mav & Number of vertebrae anterior to the first
vertebra contacting an anal fin pterygiophore (Aguirre et al.~2014) \\
Caudal Vertebra & \texttt{mcv} & Number of vertebrae posterior to and
including the first vertebra contacting an anal fin pterygiophore
(Aguirre et al.~2014) \\
Pterygiophore number & \texttt{mpt} & Number of pterygiophores anterior
to but excluding the pterygiophore under the third dorsal spine, which
is immediately anterior to and contiguous with the dorsal fin \\
Pelvic Spine length & \texttt{lps.sc} & Length from the base of one
pelvic spine above its articulation with the pelvic girdle to its distal
tip \\
Ectocoracoid & \texttt{ect.sc} & Length between the anterior and
posterior tips of the shoulder girdle base (i.e., ectocoracoid) \\
Pelvic Girdle & \texttt{tpg.sc} & Length between the anterior to
posterior tips along midline. If vestigial, the sum of longest
anterior-posterior axis for the vestiges \\
Cleithrum length & \texttt{cle.sc} & Length from free dorsal tip to
ventral tip of the cleithrum on the anterior margin of the shoulder
girdle (i.e., cleithrum) \\
Premaxilla & \texttt{pmx.sc} & Length from the anterior tip of the
premaxilla to the distal tip of the ascending process of the
premaxilla \\
Dorsal Spine & \texttt{Ds\#.sc\ \#=1/2/3} & Length from the base of a
dorsal spine above the pterygiophore to its distal tip along the
anterior edge \\
Pterygiophore & \texttt{lpt.sc} & Distance between the anterior to
posterior tips of the pterygiophore immediately preceding the 3rd dorsal
spine (when present) \\
\bottomrule()
\end{longtable}

\textcolor{red}{This table caption should be part of the table. Top row.. -YS}
Table: Traits and trait descriptions. `sc' denotes size correction of
trait against standard length. Names of bones follow Bowne
(\protect\hyperlink{ref-Bowne1994}{1994}) unless otherwise noted.

@@

@@

\toprule()

@@

\midrule()

@@

@@

\bottomrule()

@@

\caption{cle}\label{fig:unnamed-chunk-6}
\end{figure}
\begin{figure}

@@

\caption{ds1}\label{fig:unnamed-chunk-7}
\end{figure}
\begin{figure}

@@

\caption{ds2}\label{fig:unnamed-chunk-8}
\end{figure}
\begin{figure}

@@

\caption{ds3}\label{fig:unnamed-chunk-9}
\end{figure}
\begin{figure}

@@

\caption{ect}\label{fig:unnamed-chunk-10}
\end{figure}
\begin{figure}

@@

\caption{lps}\label{fig:unnamed-chunk-11}
\end{figure}
\begin{figure}

@@

\caption{lpt}\label{fig:unnamed-chunk-12}
\end{figure}
\begin{figure}

@@

\caption{maf}\label{fig:unnamed-chunk-13}
\end{figure}
\begin{figure}

@@

\caption{mav}\label{fig:unnamed-chunk-14}
\end{figure}
\begin{figure}

@@

\caption{mcv}\label{fig:unnamed-chunk-15}
\end{figure}
\begin{figure}

@@

\caption{mdf}\label{fig:unnamed-chunk-16}
\end{figure}
\begin{figure}

@@

\caption{mds}\label{fig:unnamed-chunk-17}
\end{figure}
\begin{figure}

@@

\caption{mpt}\label{fig:unnamed-chunk-18}
\end{figure}
\begin{figure}

@@

\caption{pmx}\label{fig:unnamed-chunk-19}
\end{figure}

@@

\caption{stl}\label{fig:unnamed-chunk-20}
\end{figure}

\hypertarget{references}{%
\section{References}\label{references}}

@@
